---
title: "Fatigue UC Data"
output: 
  html_notebook:
   themes: paper
   toc: yes
   toc_float: yes
editor_options: 
  chunk_output_type: inline
---

# Packages 
```{r}
library(tidyverse)
library(gtsummary)
library(ggplot2)
```

# Upload data 
```{r}
read.csv("~/University of Michigan Dropbox/Jessica Sheehan/R-Code/Fatigue Survey/MeasuringFatigueInIn-UCData111024_DATA_2024-11-30_1627.csv") -> uc_data

load("~/University of Michigan Dropbox/Jessica Sheehan/R-Code/Fatigue Survey/bmi_deid.rda") 
```

# UC Data Cleaning 
## Make gender variable 
```{r}
uc_data %>% 
  dplyr::mutate(gender = as_factor(uc_gender),
                gender = fct_recode(gender, Male = "1",
                                    Female = "2", 
                                    Other = "3",
                                    Diclose = "4"),
                gender = relevel(gender, ref = "Male")) -> uc_gender

# variable to include in final df = gender 
```

## Make age numeric only 
```{r}
uc_gender %>%
    mutate(uc_age = str_remove_all(uc_age, "years")) -> uc_age_df

uc_age_df$uc_age <- as.numeric(uc_age_df$uc_age)

names(uc_age_df)[names(uc_age_df) == "uc_age"] <- "age"

# variable to include in final df = age 
```


## Make race variable 
```{r}
uc_age_df$no_race <- (uc_age_df$uc_race___1 + uc_age_df$uc_race___2 + uc_age_df$uc_race___3 + uc_age_df$uc_race___4 + uc_age_df$uc_race___5 + uc_age_df$uc_race___6 + uc_age_df$uc_race___7)

uc_age_df %>%  
  mutate(uc_race___8 = case_when(no_race == 0 ~ '1', TRUE ~ "0")) %>% 
  mutate(uc_race___9 = case_when(no_race > 1 ~ '1', TRUE ~ "0")) -> uc_race_wide_df

uc_race_wide_df %>%
    gather(race_long, value, uc_race___1:uc_race___7, uc_race___8, uc_race___9) %>% 
    filter(value==1) %>% 
    dplyr:: select(sbj_id:age, race_long, uc_ethnicity:gender) -> uc_race_long


uc_race_long %>% 
dplyr::mutate(race_6 = as_factor(race_long),
         race_6 = fct_recode(race_6, Indian = "uc_race___1",
                              Asian = "uc_race___2", Black = "uc_race___3",
                              Native = "uc_race___4",
                              Unknown = "uc_race___5",
                              White = "uc_race___6", Other = "uc_race___7",
                              Unknown = "uc_race___8", 
                              Multi = "uc_race___9"),
         race_6 = relevel(race_6, ref = 'White')) -> uc_race_code

uc_race_code %>%
     arrange(race_6 != 'Multi') %>% 
     distinct(sbj_id, .keep_all = TRUE) -> uc_race_code_unique

uc_race_code_unique$race_6 <- factor(uc_race_code_unique$race_6,
          levels = c("Indian", "Asian", "Black", "Native", "Unknown", "White", "Other", "Multi"),
          labels = c("American Indian or Alaska Native", "Asian", "Black or African American", "Native Hawaiian or other Pacific Islander","Unknown", "White", "Other", "Multiracial")) 


uc_race_code_unique %>% 
dplyr::mutate(race_2 = as_factor(race_6),
         race_2 = fct_recode(race_2, Other = "American Indian or Alaska Native",
                              Other = "Asian", Other = "Black or African American",
                              Other = "Unknown",
                              White = "White", Other = "Other", 
                              Other = "Multiracial"),
         race_2 = relevel(race_2, ref = 'White')) -> uc_race_code_2 


uc_race_code_2$race_2 <- factor(uc_race_code_2$race_2,
          levels = c("White", "Other"),
          labels = c("White", "Other/Multi/Unknown/Did Not Disclose")) 


# variable to include in final df = race_2 and race_6 

```

## Make ethnicity variable 
```{r}
uc_race_code_2 %>% 
dplyr::mutate(ethnicity = as_factor(uc_ethnicity),
         ethnicity = fct_recode(ethnicity, Hispanic = "1",
                              Not = "2", Disclose = "3",
                              Unknown = "4"),
         ethnicity = relevel(ethnicity, ref = 'Not')) -> uc_ethnicity_df

uc_ethnicity_df$ethnicity <- factor(uc_ethnicity_df$ethnicity,
          levels = c("Hispanic", "Not", "Disclose", "Unknown"),
          labels = c("Hispanic or Latino", "Not Hispanic or Latino", "Choose not to disclose", "Unknown")) 

# variable to include in final df = ethnicity

```

## Make diagnosis variable 
```{r}
uc_ethnicity_df %>% 
dplyr::mutate(ibd_dx = as_factor(uc_ibd_type),
         ibd_dx = fct_recode(ibd_dx, CD = "2",
                             UC = "1",
                             IC = "3")) -> uc_dx_df

uc_dx_df$ibd_dx <- factor(uc_dx_df$ibd_dx,
          levels = c("CD", "UC", "IC"),
          labels = c("Crohn's disease", "Ulcerative colitis", "Indeterminant colitis")) 

# variable to include in final df = ibd_dx
```

## Complications variables 
```{r}
names(uc_dx_df)[names(uc_dx_df) == "uc_complications___1"] <- "fistula"
names(uc_dx_df)[names(uc_dx_df) == "uc_complications___2"] <- "stricture"
names(uc_dx_df)[names(uc_dx_df) == "uc_complications___3"] <- "abscess"
names(uc_dx_df)[names(uc_dx_df) == "uc_surgery"] <- "surgery"
names(uc_dx_df)[names(uc_dx_df) == "uc_hospital"] <- "hospital"

# variable to include in final df = fistula, stricture, abscess, surgery, hospital
```

## Make severity variable 
```{r}
uc_dx_df$complications <- (uc_dx_df$fistula + uc_dx_df$stricture + uc_dx_df$abscess + uc_dx_df$surgery + uc_dx_df$hospital)

uc_dx_df %>%  
mutate(severe_dx = case_when(complications > 0 ~ '1', TRUE ~ "0")) -> uc_severity_df

# variable to include in final df = severe_dx

```

## Active steroid use variable 
```{r}
names(uc_severity_df)[names(uc_severity_df) == "uc_meds_current___1"] <- "active_steroids"
```

## Current meds variable 
```{r}

uc_severity_df$multi_med <- (uc_severity_df$uc_meds_current___2 + uc_severity_df$uc_meds_current___3 + uc_severity_df$uc_meds_current___4 + uc_severity_df$uc_meds_current___5 + uc_severity_df$uc_meds_current___6 + uc_severity_df$uc_meds_current___7 + uc_severity_df$uc_meds_current___8 + uc_severity_df$uc_meds_current___9 + uc_severity_df$uc_meds_current___10 + uc_severity_df$uc_meds_current___11 + uc_severity_df$uc_meds_current___12 + uc_severity_df$uc_meds_current___13 + uc_severity_df$uc_meds_current___14 + 
uc_severity_df$uc_meds_current___15 + uc_severity_df$uc_meds_current___16)

uc_severity_df %>%  
  mutate(uc_meds_current___18 = case_when(multi_med > 1 ~ '1', TRUE ~ "0")) -> uc_meds_wide_df

uc_meds_wide_df %>%
    gather(meds_long, value_2, uc_meds_current___2:uc_meds_current___0, uc_meds_current___18) %>%
    filter(value_2==1) %>% 
    dplyr:: select(sbj_id:active_steroids, meds_long, uc_meds_prior___1:severe_dx) -> uc_meds_long

uc_meds_long %>% 
dplyr::mutate(meds_all = as_factor(meds_long),
         meds_all = fct_recode(meds_all, 
                              ASA = "uc_meds_current___2",
                              methotrexate = "uc_meds_current___3", 
                              azathioprine = "uc_meds_current___4",
                              infliximab = "uc_meds_current___5",
                              adalimumab = "uc_meds_current___6", 
                              certolizumab = "uc_meds_current___7",
                              golimumab = "uc_meds_current___8",
                              vedolizumab = "uc_meds_current___9",
                              ustekinumab = "uc_meds_current___10",
                              risankizumab = "uc_meds_current___11",
                              mirikizumab = "uc_meds_current___12",
                              etrasiod = "uc_meds_current___13",
                              ozanimod = "uc_meds_current___14",
                              tofacitinib = "uc_meds_current___15",
                              upadacitinib = "uc_meds_current___16",
                              none = "uc_meds_current___0",
                              dual= "uc_meds_current___18"),
         meds_all = relevel(meds_all, ref = 'infliximab')) -> uc_meds_code

uc_meds_code %>%
     arrange(meds_all != 'dual') %>% 
     distinct(sbj_id, .keep_all = TRUE) -> uc_meds_code_unique


uc_meds_code_unique %>% 
dplyr::mutate(meds_mech = as_factor(meds_all),
         meds_mech = fct_recode(meds_mech, 
                              ASA = "ASA",
                              Immunomodulator = "methotrexate",
                              Immunomodulator = "azathioprine",
                              TNF = "infliximab", 
                              TNF = "adalimumab",
                              TNF = "certolizumab",
                              TNF = "golimumab",
                              Integrin = "vedolizumab",
                              Interleukin = "ustekinumab",
                              Interleukin = "risankizumab",
                              Interleukin = "mirikizumab", 
                              S1P = "ozanimod",
                              S1P = "etrasiod",
                              JAK = "tofacitinib",
                              JAK = "upadacitinib", 
                              Dual = "dual",
                              none = "none"),
         meds_mech = relevel(meds_mech, ref = 'TNF')) -> uc_meds_code_2 

uc_meds_code_2 %>% 
dplyr::mutate(meds_class = as_factor(meds_all),
         meds_class = fct_recode(meds_class, 
                              ASA = "ASA",
                              Immunomodulator = "methotrexate",
                              Immunomodulator = "azathioprine",
                              Biologic = "infliximab", 
                              Biologic = "adalimumab",
                              Biologic = "certolizumab",
                              Biologic = "golimumab",
                              Biologic = "vedolizumab",
                              Biologic = "ustekinumab",
                              Biologic = "risankizumab",
                              Biologic = "mirikizumab", 
                              Small = "ozanimod",
                              Small = "etrasiod",
                              Small = "tofacitinib",
                              Small = "upadacitinib", 
                              Dual = "dual",
                              none = "none"),
         meds_class = relevel(meds_class, ref = 'Biologic')) -> uc_meds_code_3

# variable to include in final df = meds_all, meds_mech, meds_class

```

## Prednisone in the last year 
```{r}
names(uc_meds_code_3)[names(uc_meds_code_3) == "uc_prednisone"] <- "prednisone_last_year"
```

## Months of prednisone in the last year 
```{r}

uc_meds_code_3$uc_steroid_months_yr[uc_meds_code_3$uc_steroid_months_yr == "Zero"] <- '0'

names(uc_meds_code_3)[names(uc_meds_code_3) == "uc_steroid_months_yr"] <- "steroid_months_yr"

uc_meds_code_3$steroid_months_yr <- as.numeric(uc_meds_code_3$steroid_months_yr)

uc_meds_code_3$steroid_months_yr[is.na(uc_meds_code_3$steroid_months_yr)] <- 0



```


## Months of prednisone in lifetime 
```{r}

uc_meds_code_3$uc_steroid_month_life[uc_meds_code_3$uc_steroid_month_life == "24-36"] <- '30'

uc_meds_code_3 %>%
    mutate(uc_steroid_month_life = str_remove_all(uc_steroid_month_life, "months")) -> uc_steroids_df_2

names(uc_steroids_df_2)[names(uc_steroids_df_2) == "uc_steroid_month_life"] <- "steroid_month_life"

uc_steroids_df_2$steroid_month_life <- as.numeric(uc_steroids_df_2$steroid_month_life)

uc_steroids_df_2$steroid_month_life[is.na(uc_steroids_df_2$steroid_month_life)] <- 0

```

## Comorbidities
```{r}

names(uc_steroids_df_2)[names(uc_steroids_df_2) == "ucheart_liver_brain___8"] <- "psc"
names(uc_steroids_df_2)[names(uc_steroids_df_2) == "ucheart_liver_brain___11"] <- "thyroid"
names(uc_steroids_df_2)[names(uc_steroids_df_2) == "ucheart_liver_brain___13"] <- "anxiety"
names(uc_steroids_df_2)[names(uc_steroids_df_2) == "ucheart_liver_brain___14"] <- "depression"
names(uc_steroids_df_2)[names(uc_steroids_df_2) == "uc_pulmonary___4"] <- "osa"
names(uc_steroids_df_2)[names(uc_steroids_df_2) == "uc_digestive_skin___2"] <- "ibs"

```


## UC-PRO - Bowel Domain 
```{r}
# Questions include: number BM, liquid, blood, mucus, leak, urgency 

uc_steroids_df_2$uc_pro4[is.na(uc_steroids_df_2$uc_pro4)] = 0
uc_steroids_df_2$uc_pro6[is.na(uc_steroids_df_2$uc_pro6)] = 0
uc_steroids_df_2$uc_pro8[is.na(uc_steroids_df_2$uc_pro8)] = 0
uc_steroids_df_2$uc_pro12[is.na(uc_steroids_df_2$uc_pro12)] = 0

uc_steroids_df_2$uc_bowel_domain <- (uc_steroids_df_2$uc_pro1 + uc_steroids_df_2$uc_pro2 + uc_steroids_df_2$uc_pro4 + uc_steroids_df_2$uc_pro6 + uc_steroids_df_2$uc_pro8 + uc_steroids_df_2$uc_pro12)

names(uc_steroids_df_2)[names(uc_steroids_df_2) == "uc_pro1"] <- "pro_bms"
names(uc_steroids_df_2)[names(uc_steroids_df_2) == "uc_pro2"] <- "pro_liquid"
names(uc_steroids_df_2)[names(uc_steroids_df_2) == "uc_pro4"] <- "pro_blood"
names(uc_steroids_df_2)[names(uc_steroids_df_2) == "uc_pro12"] <- "pro_urgency"

# make cd bowel domain so columns match up 
uc_steroids_df_2 %>%  
  mutate(cd_bowel_domain = case_when(ibd_dx == 1 ~ 'NA', TRUE ~ "0")) -> uc_bowel_scores

uc_bowel_scores[, 168][uc_bowel_scores[, 168] == 0] <- NA

```

## CD-PRO Functional Domain 
```{r}
# questions include: gas, abdominal pain, bloating 

uc_bowel_scores$uc_pro10[is.na(uc_bowel_scores$uc_pro10)] = 0
uc_bowel_scores$uc_pro14[is.na(uc_bowel_scores$uc_pro14)] = 0
uc_bowel_scores$uc_pro16[is.na(uc_bowel_scores$uc_pro16)] = 0

uc_bowel_scores$uc_functional_domain <- (uc_bowel_scores$uc_pro10 + uc_bowel_scores$uc_pro14 + uc_bowel_scores$uc_pro16 )

names(uc_bowel_scores)[names(uc_bowel_scores) == "uc_pro14"] <- "pro_abd_pain"
names(uc_bowel_scores)[names(uc_bowel_scores) == "uc_pro16"] <- "pro_bloating"


# make uc bowel domain so columns match up 
uc_bowel_scores %>%  
  mutate(cd_functional_domain = case_when(ibd_dx == 1 ~ 'NA', TRUE ~ "0")) -> uc_functional_scores

uc_functional_scores[, 170][uc_functional_scores[, 170] == 0] <- NA

```

## Systemic Symptom 
```{r}
# questions include: joint pain, fatigue, weakness, appetite, thirst 

uc_functional_scores$uc_pro18[is.na(uc_functional_scores$uc_pro18)] = 0
uc_functional_scores$uc_pro20[is.na(uc_functional_scores$uc_pro20)] = 0
uc_functional_scores$uc_pro22[is.na(uc_functional_scores$uc_pro22)] = 0
uc_functional_scores$uc_pro24[is.na(uc_functional_scores$uc_pro24)] = 0
uc_functional_scores$uc_pro26[is.na(uc_functional_scores$uc_pro26)] = 0

uc_functional_scores$systemic_score <- (uc_functional_scores$uc_pro18 + uc_functional_scores$uc_pro20 + uc_functional_scores$uc_pro22 + uc_functional_scores$uc_pro24 + uc_functional_scores$uc_pro26)

names(uc_functional_scores)[names(uc_functional_scores) == "uc_pro18"] <- "pro_joint_pain"
names(uc_functional_scores)[names(uc_functional_scores) == "uc_pro20"] <- "pro_fatigue"
names(uc_functional_scores)[names(uc_functional_scores) == "uc_pro24"] <- "pro_weak"

# don't need to make a uc systemic symptoms score because it is the same 

```

## Coping Domain 
```{r}
# questions include: schedule, eat less, avoid foods, OTC, did you leave home (yes - access to bathroom and wipes) (no - did you not leave home bc of uc)

uc_functional_scores$uc_pro32[is.na(uc_functional_scores$uc_pro32)] = 0
uc_functional_scores$uc_pro33[is.na(uc_functional_scores$uc_pro33)] = 0
uc_functional_scores$uc_pro34[is.na(uc_functional_scores$uc_pro34)] = 0

uc_functional_scores$coping_score <- (uc_functional_scores$uc_pro27 + uc_functional_scores$uc_pro28 + uc_functional_scores$uc_pro29 + uc_functional_scores$uc_pro30 + uc_functional_scores$uc_pro32 + uc_functional_scores$uc_pro33 + uc_functional_scores$uc_pro34)


```

## Daily Life Impact 
```{r}
# questions include: work/school, chores, enjoyment, sleep, concentrate, leaving, travel, sex, plan

uc_functional_scores$daily_impact <- (uc_functional_scores$uc_pro35 + uc_functional_scores$uc_pro36 + uc_functional_scores$uc_pro37 + uc_functional_scores$uc_pro38 + uc_functional_scores$uc_pro39 + uc_functional_scores$uc_pro40 + uc_functional_scores$uc_pro41 +
uc_functional_scores$uc_pro42 + uc_functional_scores$uc_pro43)

names(uc_functional_scores)[names(uc_functional_scores) == "uc_pro39"] <- "pro_concentrate"
names(uc_functional_scores)[names(uc_functional_scores) == "uc_pro38"] <- "pro_sleep"
```

## Emotional Impact 
```{r}
# questions include: alone, embarrassed, worried, scared, control, angry, frustrated, depressed 

uc_functional_scores$emotional_impact <- (uc_functional_scores$uc_pro44 + uc_functional_scores$uc_pro45 + uc_functional_scores$uc_pro46 + uc_functional_scores$uc_pro47 + uc_functional_scores$uc_pro48 + uc_functional_scores$uc_pro49 + uc_functional_scores$uc_pro50 +
uc_functional_scores$uc_pro51)

names(uc_functional_scores)[names(uc_functional_scores) == "uc_pro51"] <- "pro_depressed"
```

## FACIT-F Scoring 
## FACIT-F Scoring
```{r}

names(uc_functional_scores)[names(uc_functional_scores) == "uc_facit_q7"] <- "facit_7"
names(uc_functional_scores)[names(uc_functional_scores) == "uc_facit_q8"] <- "facit_8"

uc_facit_scores <- uc_functional_scores %>%
  mutate(across(contains("uc_facit"), ~
                  as.numeric(dplyr::recode(.x, `0` = "4", `1` = "3", `2` = "2", `3` = "1", `4` = "0"))))

names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q1"] <- "facit_1"
names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q2"] <- "facit_2"
names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q3"] <- "facit_3"
names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q4"] <- "facit_4"
names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q5"] <- "facit_5"
names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q6"] <- "facit_6"
names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q9"] <- "facit_9"
names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q10"] <- "facit_10"
names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q11"] <- "facit_11"
names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q12"] <- "facit_12"
names(uc_facit_scores)[names(uc_facit_scores) == "uc_facit_q13"] <- "facit_13"


uc_facit_scores$facit_total <- (uc_facit_scores$facit_1 + uc_facit_scores$facit_2 + uc_facit_scores$facit_3 + uc_facit_scores$facit_4 + uc_facit_scores$facit_5 + uc_facit_scores$facit_6 + uc_facit_scores$facit_7 + uc_facit_scores$facit_8 + uc_facit_scores$facit_9 + uc_facit_scores$facit_10 + uc_facit_scores$facit_11 + uc_facit_scores$facit_12 + uc_facit_scores$facit_13)

uc_facit_scores %>%  
  mutate(facit_fatigue = case_when(facit_total < 30 ~ '1', TRUE ~ "0")) -> uc_facit_scores_total
                
```

## IBD-F 
```{r}

uc_facit_scores_total$ibd_f_total <- 
(uc_facit_scores_total$uc_ibdf_1 + 
 uc_facit_scores_total$uc_ibdf_2 +
 uc_facit_scores_total$uc_ibdf_3 + 
 uc_facit_scores_total$uc_ibdf_4 +
 uc_facit_scores_total$uc_ibdf_5) 

```

## Replace stop bang BMI question with actual BMI > 35
```{r}

left_join(uc_facit_scores_total, bmi_deid, by = "sbj_id") -> uc_fatigue_bmi
            
uc_fatigue_bmi %>% 
  mutate(bmi_sb = case_when(BMI > 35 ~ '1', TRUE ~ "0")) -> uc_bmi
```

## STOP BANG
```{r}
uc_bmi %>% 
  dplyr::mutate(snore_sb = as_factor(uc_stop_bang1),
                snore_sb = fct_recode(snore_sb, 
                                     "0" = "0",
                                    "1" = "1", 
                                    "0" = "2"),
                snore_sb = relevel(snore_sb, ref = "0")) -> uc_stop_bang_1 

uc_stop_bang_1 %>% 
  dplyr::mutate(sleepy_sb = as_factor(uc_stop_bang2),
                sleepy_sb = fct_recode(sleepy_sb, 
                                     "0" = "0",
                                    "1" = "1"), 
                sleepy_sb = relevel(sleepy_sb, ref = "0")) -> uc_stop_bang_2  

uc_stop_bang_2 %>% 
  dplyr::mutate(choking_sb = as_factor(uc_stop_bang3),
                choking_sb = fct_recode(choking_sb, 
                                      "0" = "0",
                                    "1" = "1", 
                                    "0" = "2"), 
                choking_sb = relevel(choking_sb, ref = "0")) -> uc_stop_bang_3
  
uc_stop_bang_3 %>% 
    dplyr::mutate(htn_sb = as_factor(uc_stop_bang4),
                htn_sb = fct_recode(htn_sb, 
                                      "0" = "0",
                                    "1" = "1", 
                                    "0" = "2"), 
                htn_sb = relevel(htn_sb, ref = "0")) -> uc_stop_bang_4


uc_stop_bang_4 %>% 
  dplyr::mutate(age_50_sb = as_factor(uc_stop_bang6),
                age_50_sb = fct_recode(age_50_sb, 
                                      "0" = "0",
                                    "1" = "1"),
                age_50_sb = relevel(age_50_sb, ref = "0")) -> uc_stop_bang_6

uc_stop_bang_6 %>% 
    dplyr::mutate(neck_sb = as_factor(uc_stop_bang7),
                neck_sb = fct_recode(neck_sb, 
                                      "0" = "0",
                                    "1" = "1", 
                                    "0" = "2"), 
                neck_sb = relevel(neck_sb, ref = "0")) -> uc_stop_bang_7

uc_stop_bang_7 %>% 
      dplyr::mutate(male_sb = as_factor(uc_stop_bang8),
                male_sb = fct_recode(male_sb, 
                                      "0" = "0",
                                    "1" = "1", 
                                    "0" = "2"), 
                male_sb = relevel(male_sb, ref = "0")) -> uc_stop_bang_8
  
```


## STOPBANG total 
```{r}

uc_stop_bang_8$snore_sb <- as.integer(uc_stop_bang_8$snore_sb) - 1
uc_stop_bang_8$sleepy_sb <- as.integer(uc_stop_bang_8$sleepy_sb) - 1
uc_stop_bang_8$choking_sb <- as.integer(uc_stop_bang_8$choking_sb) - 1
uc_stop_bang_8$htn_sb <- as.integer(uc_stop_bang_8$htn_sb) - 1
uc_stop_bang_8$bmi_sb <- as.integer(uc_stop_bang_8$bmi_sb) 
uc_stop_bang_8$age_50_sb <- as.integer(uc_stop_bang_8$age_50_sb) - 1
uc_stop_bang_8$neck_sb <- as.integer(uc_stop_bang_8$neck_sb) - 1
uc_stop_bang_8$male_sb <- as.integer(uc_stop_bang_8$male_sb) - 1

uc_stop_bang_8$stop_bang_total <- (uc_stop_bang_8$snore_sb + uc_stop_bang_8$sleepy_sb + uc_stop_bang_8$choking_sb + uc_stop_bang_8$htn_sb + uc_stop_bang_8$bmi_sb + uc_stop_bang_8$age_50_sb + uc_stop_bang_8$neck_sb + uc_stop_bang_8$male_sb)
  
uc_stop_bang_8 %>%  
  mutate(osa_mod_high = case_when(stop_bang_total > 2 ~ '1', TRUE ~ "0")) %>% 
  mutate(osa_high = case_when(stop_bang_total > 4 ~ '1', TRUE ~ "0")) -> uc_stop_bang_high

```

## Final uc data frame 
```{r}
uc_stop_bang_high %>% dplyr::select(sbj_id, ibd_dx, age, gender, race_6, race_2, ethnicity, BMI, fistula, stricture, abscess, surgery, hospital, severe_dx, active_steroids, prednisone_last_year, steroid_months_yr, steroid_month_life, meds_all, meds_mech, meds_class, psc, thyroid, anxiety, depression, osa, ibs, pro_bms, pro_liquid, pro_blood, pro_urgency, pro_abd_pain, pro_bloating, pro_joint_pain, pro_fatigue, pro_sleep, pro_weak, pro_concentrate, pro_depressed, cd_bowel_domain, uc_bowel_domain, cd_functional_domain, uc_functional_domain, systemic_score, coping_score, daily_impact, emotional_impact, facit_1:facit_13,facit_total, facit_fatigue, ibd_f_total, bmi_sb:male_sb, stop_bang_total, osa_mod_high, osa_high) -> uc_final 
```


# Save Data Frame 
```{r}
save(uc_final, file = "~/University of Michigan Dropbox/Jessica Sheehan/R-Code/Fatigue Survey/uc_final.rda")
```



