---
title: "Fatigue Analysis"
output:
  html_document:
    toc: true
    df_print: paged
  html_notebook:
    themes: paper
    toc: true
    toc_float: true
editor_options:
  chunk_output_type: inline
---

# Packages 
```{r}
library(tidyverse)
library(gtsummary)
library(ggplot2)
library(broom) 
library(performance)
library(glmtoolbox)
library(DescTools)
library(here)
library(corrplot)
library(broom)
library(pROC)
library(expss)
library(here)
```

# Upload data 
```{r}
load(here("cd_final.rda"))
load(here("uc_final.rda"))
```

# Join Data 
```{r}
rbind(cd_final, uc_final) -> ibd_all

save(ibd_all, file = here("ibd_all.rda"))
```

# Filter small numbers 
```{r}
ibd_all %>% filter(gender != "Other") %>% 
            filter(gender != "Diclose") -> ibd_pts 
```

# Determine cutoff score on IBD_F 
```{r}
#print(IQR(ibd_pts$ibd_f_total))
#res<-quantile(ibd_pts$ibd_f_total, probs = c(0,0.25,0.5,0.75,1))
#print(res)
# 12 seems to be a reasonable cut off for significant fatigue 
```

# Make variable for clinically significant fatigue based on IBD-F
```{r}
ibd_pts %>% 
mutate(ibd_f_fatigue = case_when(ibd_f_total >= 12 ~ '1', TRUE ~ "0")) ->ibd_pts

ibd_pts$ibd_f_fatigue <- as.numeric(ibd_pts$ibd_f_fatigue)
```


# Labels 
```{r}
ibd_pts = apply_labels(ibd_pts,
                      sbj_id = "Subject ID",
                      ibd_dx = "IBD Diagnosis",
                      age = "Age",
                      gender = "Sex",
                      race_6 = "Race",
                      ethnicity = "Ethnicity",
                      severe_dx = "Moderate-to-Severe IBD",
                      active_steroids = "Active Corticosteroid Use",
                      prednisone_last_year = "Prednisone in the Last year",
                      steroid_months_yr = "Total Months of Steroids in the Last Year",
                      steroid_month_life = "Total Months of Steroids in Lifetime",
                      meds_class = "IBD Medications",
                      anxiety = "Self-Reported Anxiety Diagnosis",
                      depression = "Self-Reported Depression Diagnosis",
                      osa = "Obstructive Sleep Apnea",
                      pro_fatigue = "Fatigue PRO Score",
                      pro_sleep = "Sleep PRO Score", 
                      pro_concentrate = "Concentration PRO Score",
                      facit_total = "FACIT-F Score",
                      facit_fatigue = "FACIT-F < 30",
                      ibd_f_total = "IBD-F Score",
                      ibd_f_fatigue = "IBD-F > 12",
                      stop_bang_total = "STOPBANG Score",
                      osa_mod_high = "Intermediate to High Risk for OSA",
                      osa_high = "High Risk of OSA")
```


# Demographics 
```{r}
ibd_pts %>% dplyr::select(ibd_dx, age, gender, race_6, ethnicity, BMI, severe_dx, active_steroids, prednisone_last_year, steroid_months_yr, steroid_month_life, meds_class, anxiety, depression, osa, pro_fatigue, pro_sleep, pro_concentrate, facit_total, facit_fatigue, ibd_f_total, ibd_f_fatigue, bmi_sb, stop_bang_total, osa_mod_high, osa_high, pro_concentrate) -> ibd_demo 

na.omit(ibd_demo) -> ibd_demo_all

ibd_demo_all$severe_dx <- as.numeric(ibd_demo_all$severe_dx)
ibd_demo_all$osa_mod_high <- as.numeric(ibd_demo_all$osa_mod_high)
ibd_demo_all$osa_high <- as.numeric(ibd_demo_all$osa_high)
ibd_demo_all$facit_fatigue <- as.numeric(ibd_demo_all$facit_fatigue)
ibd_demo_all$steroid_months_yr <- as.numeric(ibd_demo_all$steroid_months_yr)
ibd_demo_all$steroids_month_life <- as.numeric(ibd_demo_all$steroid_month_life)
ibd_demo_all$pro_fatigue <- as.numeric(ibd_demo_all$pro_fatigue)
ibd_demo_all$pro_sleep <- as.numeric(ibd_demo_all$pro_sleep)
ibd_demo_all$pro_concentrate <- as.numeric(ibd_demo_all$pro_concentrate)
ibd_demo_all$BMI <- as.numeric(ibd_demo_all$BMI)

ibd_demo_all %>% tbl_summary(
        statistic = list(all_continuous() ~ "{mean} ({sd})"),
        type = list(steroid_months_yr ~ "continuous"),
        missing_text = "(Missing)")
```

# Look at subgroups based on risk stratification  
```{r}
# high risk 
ibd_demo_all %>% filter(osa_high != "0") %>% 
  dplyr::select(ibd_dx, age, gender, race_6, ethnicity, BMI, severe_dx, active_steroids, steroid_months_yr, steroid_month_life, meds_class, anxiety, depression, osa, pro_fatigue, facit_total, facit_fatigue, ibd_f_total, stop_bang_total, osa_mod_high, osa_high) -> osa_high_risk 
osa_high_risk %>% tbl_summary(
        statistic = list(all_continuous() ~ "{mean} ({sd})"),
        missing_text = "(Missing)")

# moderate risk
ibd_demo_all$mod_osa <- 0; ibd_demo_all[ibd_demo_all$stop_bang_total > 2 & ibd_demo_all$stop_bang_total < 5, "mod_osa"] <- 1

ibd_demo_all %>% filter(mod_osa != "0") %>% 
  dplyr::select(ibd_dx, age, gender, race_6, ethnicity, BMI, severe_dx, active_steroids, steroid_months_yr, steroid_month_life, meds_class, anxiety, depression, osa, pro_fatigue, facit_total, facit_fatigue, ibd_f_total, stop_bang_total, osa_mod_high, osa_high) -> osa_mod_high_risk 
osa_mod_high_risk %>% tbl_summary(
        statistic = list(all_continuous() ~ "{mean} ({sd})"),
        missing_text = "(Missing)")

## Look at what proportion of these people actually got sleep studies 

# low risk 
ibd_demo_all %>% filter(osa_mod_high != "1") %>% 
  dplyr::select(ibd_dx, age, gender, race_6, ethnicity, BMI, severe_dx, active_steroids, steroid_months_yr, steroid_month_life, meds_class, anxiety, depression, osa, pro_fatigue, facit_total, facit_fatigue, ibd_f_total, stop_bang_total, osa_mod_high, osa_high) -> osa_low_risk
osa_low_risk %>% tbl_summary(
        statistic = list(all_continuous() ~ "{mean} ({sd})"),
        missing_text = "(Missing)")

```


# Overall OSA Risk 
## Univariate Analysis moderate to high risk 
```{r}

ibd_demo_all$osa_mod_high <- as.numeric(ibd_demo_all$osa_mod_high)

ibd_demo_all %>% tbl_summary(
        by = "osa_mod_high", 
        statistic = list(all_continuous() ~ "{mean} ({sd})"),
        type = list(steroid_months_yr ~ "continuous"),
        missing_text = "(Missing)") %>% 
        add_p()

ibd_demo_all %>% 
  tbl_uvregression(
    method = glm,
    y = osa_mod_high,
    include = c(ibd_dx, age, gender, BMI, severe_dx, active_steroids, prednisone_last_year, steroid_months_yr, steroid_month_life, meds_class, anxiety, depression, facit_fatigue, ibd_f_total, ibd_f_fatigue, pro_fatigue,  pro_sleep, pro_concentrate),
    method.args = list(family = binomial),
    type = list(steroid_months_yr ~ "continuous"),
    exponentiate = TRUE,
  ) 
# removed pro_fatigue_2

```

## Multivariable Analysis for moderate to high risk 
```{r}
ibd_demo_all$osa_mod_high <- as.numeric(ibd_demo_all$osa_mod_high)
osa_risk <- glm(osa_mod_high ~ age + gender + BMI + steroid_months_yr,
              family = "binomial", 
              data = ibd_demo_all)


summary(osa_risk )
broom::glance(osa_risk )
broom::tidy(osa_risk , exponentiate = TRUE)
tbl_regression(osa_risk, exponentiate = TRUE)

# C-Statistic/AUROC 
Cstat(osa_risk)

# Model performance 
model_performance(osa_risk)
performance::check_model(osa_risk)


```



## Univariate model high risk 
```{r}
ibd_demo_all$osa_high <- as.numeric(ibd_demo_all$osa_high)

ibd_demo_all %>% tbl_summary(
        by = "osa_high", 
        statistic = list(all_continuous() ~ "{mean} ({sd})"),
        type = list(steroid_months_yr ~ "continuous"),
        missing_text = "(Missing)") %>% 
        add_p()

ibd_demo_all %>% 
  tbl_uvregression(
    method = glm,
    y = osa_high,
    include = c(ibd_dx, age, gender, BMI, severe_dx, active_steroids,prednisone_last_year, steroid_months_yr, steroid_month_life, meds_class, anxiety, depression, facit_fatigue, ibd_f_total, pro_fatigue, pro_sleep, pro_concentrate),
    method.args = list(family = binomial),
    type = list(steroid_months_yr ~ "continuous"),
    exponentiate = TRUE,
  ) 
```




## Multivariable model for high risk 
```{r}
ibd_demo_all$osa_high <- as.numeric(ibd_demo_all$osa_high)
osa_high_risk <- glm(osa_high ~ age + gender + BMI + pro_fatigue + pro_concentrate + steroid_months_yr,
              family = "binomial", 
              data = ibd_demo_all)


summary(osa_high_risk )
broom::glance(osa_high_risk )
broom::tidy(osa_high_risk , exponentiate = TRUE)
tbl_regression(osa_high_risk, exponentiate = TRUE)

# C-Statistic/AUROC 
Cstat(osa_high_risk)

# Model performance 
model_performance(osa_high_risk)
performance::check_model(osa_high_risk)


```


# Intermediate-High Risk with NO OSA DX 
## Demographics 
```{r}
ibd_demo_all$osa_mod_high <- as.numeric(ibd_demo_all$osa_mod_high )

# make variable for OSA risk without a diagnosis 
ibd_demo_all$mod_osa_no_dx <- 0; ibd_demo_all[ibd_demo_all$osa_mod_high >= 1 & ibd_demo_all$osa < 1, "mod_osa_no_dx"] <- 1

ibd_demo_all %>% dplyr::select(osa, osa_mod_high, mod_osa_no_dx) -> osa_variables

ibd_demo_all$mod_osa_no_dx <- as.numeric(ibd_demo_all$mod_osa_no_dx)

ibd_demo_all %>% 
mutate(pro_fatigue_2 = case_when(pro_fatigue > 1 ~ '1', TRUE ~ "0")) ->ibd_demo_all

ibd_demo_all$pro_fatigue_2 <- as.numeric(ibd_demo_all$pro_fatigue_2)

# Demographics 
ibd_demo_all %>% filter(mod_osa_no_dx != "0") %>% 
  dplyr::select(ibd_dx, age, gender, race_6, ethnicity, severe_dx, active_steroids, steroid_months_yr, steroid_month_life, meds_class, anxiety, depression, osa, facit_total, facit_fatigue, ibd_f_total, pro_fatigue, pro_fatigue_2,  pro_sleep, pro_concentrate, stop_bang_total) -> osa_mod_high_risk 
osa_mod_high_risk %>% tbl_summary(
        statistic = list(all_continuous() ~ "{mean} ({sd})"),
        missing_text = "(Missing)")
```

## Univeriate Analysis 
```{r}
ibd_demo_all %>% filter(osa == "0") %>% tbl_summary(
        by = "mod_osa_no_dx", 
        statistic = list(all_continuous() ~ "{mean} ({sd})"),
        type = list(steroid_months_yr ~ "continuous",
                    pro_fatigue ~ "continuous",
                    pro_concentrate ~ "continuous",
                    pro_sleep ~ "continuous"),
        missing_text = "(Missing)") %>% 
        add_p()

ibd_demo_all %>% filter(osa == "0") %>% tbl_uvregression(
    method = glm,
    y = mod_osa_no_dx,
    include = c(ibd_dx, age, gender, severe_dx, active_steroids, prednisone_last_year, steroid_months_yr, steroid_month_life, meds_class, anxiety, depression, facit_fatigue, ibd_f_total, ibd_f_fatigue, pro_fatigue, pro_sleep, pro_concentrate),
    method.args = list(family = binomial),
    exponentiate = TRUE,
  ) 
```

## Multviariable analysis 
```{r}
library(sjmisc)
ibd_demo_all %>% filter(osa == "0") -> ibd_no_osa

# set_label(ibd_no_osa$mod_osa_no_dx) <- "Predictors of Increased Risk for OSA"

osa_no_dx <- glm(mod_osa_no_dx ~ age + gender +  BMI + active_steroids + facit_fatigue,
              family = "binomial", 
              data = ibd_no_osa)


summary(osa_no_dx )
broom::glance(osa_no_dx )
broom::tidy(osa_no_dx , exponentiate = TRUE)
tbl_regression(osa_no_dx, exponentiate = TRUE)

# C-Statistic/AUROC 
Cstat(osa_no_dx)

# Model performance 
model_performance(osa_no_dx)
performance::check_model(osa_no_dx)

```
## Plot model 
```{r}
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(ggplot2)

plot_model(osa_no_dx) + scale_y_log10(limits = c(0.01, 50)) 

ggsave(here('osa_no_dx.jpeg'))
```


# Compare people diagnosed with OSA vs no diagnosis of OSA 
## Univariate analysis 
```{r}
ibd_demo_all %>% filter(osa_high != "0")


ibd_demo_all$stop_bang_total <- as.numeric(ibd_demo_all$stop_bang_total)

ibd_demo_all %>% tbl_summary(
        by = "osa", 
        statistic = list(all_continuous() ~ "{mean} ({sd})"),
        type = list(steroid_months_yr ~ "continuous"),
        missing_text = "(Missing)") %>% 
        add_p()

ibd_demo_all %>% 
  tbl_uvregression(
    method = glm,
    y = osa,
    include = c(ibd_dx, age, gender, severe_dx, active_steroids, prednisone_last_year, steroid_months_yr, steroid_month_life, meds_class, anxiety, depression, facit_fatigue, ibd_f_total, pro_fatigue, pro_sleep, pro_concentrate),
    method.args = list(family = binomial),
    exponentiate = TRUE,
  ) 
```

## Multivariable model 
```{r}
# STOPBANG AlONE
osa_1 <- glm(osa ~ stop_bang_total,
              family = "binomial", 
              data = ibd_demo_all)

summary(osa_1 )
broom::glance(osa_1 )
broom::tidy(osa_1 , exponentiate = TRUE)
tbl_regression(osa_1, exponentiate = TRUE)

# C-Statistic/AUROC 
Cstat(osa_1)

# Model performance 
model_performance(osa_1)
performance::check_model(osa_1)

# STOP BANG PLUS
osa_2 <- glm(osa ~ stop_bang_total + steroid_months_yr + pro_fatigue + pro_sleep + pro_concentrate,
              family = "binomial", 
              data = ibd_demo_all)

summary(osa_2 )
broom::glance(osa_2 )
broom::tidy(osa_2 , exponentiate = TRUE)
tbl_regression(osa_2, exponentiate = TRUE)

# C-Statistic/AUROC 
Cstat(osa_2)

# Model performance 
model_performance(osa_2)
performance::check_model(osa_2)

```



    



Predicting Fatigue with PRO_fatigue 
____________________________________________________________________

# IBD_F 
```{r}
print(IQR(ibd_demo_all$ibd_f_total))
res<-quantile(ibd_demo_all$ibd_f_total, probs = c(0,0.25,0.5,0.75,1))
print(res)
# 12 seems to be a reasonable cut off for significant fatigue 
```

# Make variable for clinically significant fatigue based on IBD-F
```{r}
ibd_demo_all %>% 
mutate(ibd_f_fatigue = case_when(ibd_f_total >= 12 ~ '1', TRUE ~ "0")) ->ibd_demo_all

ibd_demo_all$ibd_f_fatigue <- as.numeric(ibd_demo_all$ibd_f_fatigue)
```

# Correlations
```{r}
correlation1 <- cor(ibd_demo_all$facit_total, ibd_demo_all$ibd_f_total, method = 'pearson')
correlation1

correlation2 <- cor(ibd_demo_all$facit_total, ibd_demo_all$pro_fatigue, method = 'pearson')
correlation2

correlation3 <- cor(ibd_demo_all$ibd_f_total, ibd_demo_all$pro_fatigue, method = 'pearson')
correlation3

correlation4 <- cor(ibd_demo_all$facit_fatigue, ibd_demo_all$pro_fatigue, method = 'pearson')
correlation4

correlation5 <- cor(ibd_demo_all$ibd_f_fatigue, ibd_demo_all$pro_fatigue, method = 'pearson')
correlation5

correlation6 <- cor(ibd_demo_all$ibd_f_fatigue, ibd_demo_all$facit_fatigue, method = 'pearson')
correlation6

```

# Pro_fatigue and FACIT-F 
```{r}

roc_facit_f <- roc(ibd_demo_all$facit_fatigue, ibd_demo_all$pro_fatigue)
roc_facit_f
coords(roc_facit_f)
plot.roc(roc_facit_f)
coords(roc_facit_f, "best", ret=c("threshold", "sens", "spec", "ppv", "npv"))
coords(roc_facit_f, "local maximas", ret=c("threshold", "sens", "spec", "ppv", "npv"))

ci(roc_facit_f, of = "thresholds", thresholds = 1)
ci(roc_facit_f, of = "thresholds", thresholds = 2)
ci(roc_facit_f, of = "thresholds", thresholds = 3)

roc_facit_f_plot <- plot.roc(ibd_demo_all$facit_fatigue, ibd_demo_all$pro_fatigue,
                   main = "FACIT-F", 
                   percent=TRUE,
                   ci = TRUE,                  # compute AUC (of AUC by default)
                   print.auc = TRUE)           # print the AUC (will contain the CI)
ciobj <- ci.se(roc_facit_f_plot,                         # CI of sensitivity
               specificities = seq(0, 100, 5)) # over a select set of specificities
plot(ciobj, type = "shape", col = "#1c61b6AA")     # plot as a blue shape
plot(ci(roc_facit_f_plot, of = "thresholds", thresholds = "best")) # add one threshold

```

# PRO-fatigue and IBD-F 
```{r}
roc_ibd_f <- roc(ibd_demo_all$ibd_f_fatigue, ibd_demo_all$pro_fatigue)
roc_ibd_f
coords(roc_ibd_f)
plot.roc(roc_ibd_f)
coords(roc_ibd_f, "best", ret=c("threshold", "sens", "spec", "ppv", "npv"))
coords(roc_ibd_f, "local maximas", ret=c("threshold", "sens", "spec", "ppv", "npv"))

ci(roc_ibd_f, of = "thresholds", thresholds = 1)
ci(roc_ibd_f, of = "thresholds", thresholds = 2)
ci(roc_ibd_f, of = "thresholds", thresholds = 3)

roc_ibd_f_plot <- plot.roc(ibd_demo_all$ibd_f_fatigue, ibd_demo_all$pro_fatigue,
                   main = "IBD-F", 
                   percent=TRUE,
                   ci = TRUE,                  # compute AUC (of AUC by default)
                   print.auc = TRUE)           # print the AUC (will contain the CI)
ciobj <- ci.se(roc_facit_f_plot,                         # CI of sensitivity
               specificities = seq(0, 100, 5)) # over a select set of specificities
plot(ciobj, type = "shape", col = "#1c61b6AA")     # plot as a blue shape
plot(ci(roc_facit_f_plot, of = "thresholds", thresholds = "best")) # add one threshold
```

# factors associated with fatigue (FACIT-F)
```{r}
fatigue_1 <- glm(facit_fatigue ~ ibd_dx + age + gender + severe_dx + active_steroids + anxiety + depression,
              family = "binomial", 
              data = ibd_demo_all)


summary(fatigue_1 )
broom::glance(fatigue_1 )
broom::tidy(fatigue_1 , exponentiate = TRUE)
tbl_regression(fatigue_1, exponentiate = TRUE) -> facit_f_table
print(facit_f_table)

# C-Statistic/AUROC 
Cstat(fatigue_1)

# Model performance 
model_performance(fatigue_1)
performance::check_model(fatigue_1)
```

# factors predicting fatigue on IBD-F
```{r}
ibd_demo_all$ibd_f_fatigue <- as.numeric(ibd_demo_all$ibd_f_fatigue)
fatigue_2 <- glm(ibd_f_fatigue ~ ibd_dx + age + gender + severe_dx + active_steroids + anxiety + depression,
              family = "binomial", 
              data = ibd_demo_all)


summary(fatigue_2 )
broom::glance(fatigue_2 )
broom::tidy(fatigue_2 , exponentiate = TRUE)
tbl_regression(fatigue_2, exponentiate = TRUE) -> ibd_f_table
print(ibd_f_table)

# C-Statistic/AUROC 
Cstat(fatigue_2)

# Model performance 
model_performance(fatigue_2)
performance::check_model(fatigue_2)
```

# Combine tables 
```{r}
fatigue_tables <-
  tbl_merge(
    tbls = list(facit_f_table, ibd_f_table),
    tab_spanner = c("**FACIT-F**", "**IBD-F**"))
print(fatigue_tables)
```



